Classless Java: Tuning Java Interfaces

### 2016-03-20 OOPSLA16/sections/Implementation.tex
local changes

That is, Java libraries can interact with the Java compilation process,
acting as a man in the middle between the 
generation of the abstract syntax tree and the Java Bytecode.
\marco{is this correct?}
This process is facilitated by frameworks like Lombock~\cite{lombok}:
a Java library that aims at removing (or
reducing) Java boilerplate code via
annotations.
Figure~\ref{fig:lombok}\haoyuan{Wrong ref?} illustrates the
flow of \mixin annotation processing in Lombok.
%There are a number of annotations provided by the
%original Lombok, including \Q:@Getter:, \Q:@Setter:,
%\Q:@ToString: for generating getters, setters and \QM{toString}
%methods, respectively.  Furthermore, Lombok provides a number of
%interfaces for users to create custom transformations, as extensions
%to the original framework.
%A transformation is based on a handler, which acts on the AST for the
%annotated node and returns a modified AST for analysis and
%generation afterwards. Such a handler can either be a Javac handler or
%an Eclipse handler.

>>>>

That is, Java libraries can interact with the Java compilation process,
acting as a man in the middle between the 
generation of the abstract syntax tree and the Java Bytecode.
\marco{is this correct?}
This process is facilitated by frameworks like Lombock~\cite{lombok}:
a Java library that aims at removing (or
>>>>>>> 769243b65e4aa45abf264bc79b016c61525e225f
reducing) Java boilerplate code via
annotations.
Figure~\ref{fig:lombok}\haoyuan{Wrong ref?} illustrates the
flow of \mixin annotation processing in Lombok.
%There are a number of annotations provided by the
%original Lombok, including \Q:@Getter:, \Q:@Setter:,
%\Q:@ToString: for generating getters, setters and \QM{toString}
%methods, respectively.  Furthermore, Lombok provides a number of
%interfaces for users to create custom transformations, as extensions
%to the original framework.
%A transformation is based on a handler, which acts on the AST for the
%annotated node and returns a modified AST for analysis and
%generation afterwards. Such a handler can either be a Javac handler or
%an Eclipse handler.
